The problem and promise of scale in multilayer networks

### 2019-09-26 paper/table1.Rmd
drop toc

---
output: 
  github_document:
    toc: true
author: Alec Robitaille, Quinn M.R. Webber, Julie Turner and Eric Vander Wal
date: "-- `r Sys.Date()`"
---

@@

In table 1, we define three types of multilayer networks that incorporate spatial variables. 
How are layers defined, nodes defined, inter layer edges

>>>>

---
output: github_document
author: Alec Robitaille, Quinn M.R. Webber, Julie Turner and Eric Vander Wal
date: "-- `r Sys.Date()`"
---

@@

In table 1, we define three types of multilayer networks that *can* incorporate spatial variables.

Multilayer networks are composed of layers, nodes, interlayer edges and intralayer edges. Layers are

How are layers defined, nodes defined, inter layer edges
